Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/study.tex
revert use of macro
use LHS instead of l.h.s.

\noindent
We revisit each hypothesis and show the related data and conclusions.
%
\begin{enumerate}
\item Computations involving loops over arrays are common, where an
  arrays are read from with a static pattern based on constant offsets
  from (base or dervied) induction variables;
\end{enumerate}
%
We identified \num{\overalltickAssign} instances of assignments within loops in
which an array subscript flows to the right-hand side. We refer
to each one of these as an \emph{array computation}.
We performed the classification described above
and grouped the data by the right-hand side classification only:
%%
\begin{center}
\begin{tabular}{l|S[table-format=4]@{\extracolsep{5pt}}S[table-format=2.2]c}
\textbf{RHS classification} & \textbf{Number} & \% &
\textit{grouping 1} \\ \hline
Affine                          & 34        & 0.03\%
& \multirow{3}{*}{81.43\%} \\ \cline{1-3}
Neighbourhood                   & 65334     & 60.06 \%  \\ \cline{1-3}
Neighbourhood + absolute       & 23209     & 21.34\%  \\ \hline
Other                           & 20196     & 18.57 \%  \\ \hline \hline
\textbf{Total}                  & 108773    & 100\% \\
\end{tabular}
\end{center}
%
\noindent
Since, affine and neighbour patterns are static, we group them
(\textit{grouping 1}) to see that $81.43\%$ of the array computations
(88,577) have a static pattern that comprises constant offsets of
base/derived induction variables (potential with some absolute
indices), confirming \emph{hypothesis 1}. Note that affine subscripts
are rare, perhaps due to programmers relying on compilers for
optimisation rather than hand optimising (which tends to lead to
affine indices).  Overwhelmingly, the main category is neighbourhood
offsets (possibly mixed with constants in some dimensions). The
``affine + absolute'' class is not represented at all. \marginpar{\mnote{(2)
  Mention what sort of things are included in other.}}

@@

The most common category has an l.h.s array subscript

>>>>

\noindent
We revisit each hypothesis and show the related data and conclusions.
%
\begin{enumerate}
\item Computations involving loops over arrays are common, where an
  arrays are read from with a static pattern based on constant offsets
  from (base or dervied) induction variables;
\end{enumerate}
%
We identified \num{108773} instances of assignments within loops in
which an array subscript flows to the right-hand side. We refer
to each one of these as an \emph{array computation}.
We performed the classification described above
and grouped the data by the right-hand side classification only:
%%
\begin{center}
\begin{tabular}{l|S[table-format=4]@{\extracolsep{5pt}}S[table-format=2.2]c}
\textbf{RHS classification} & \textbf{Number} & \% &
\textit{grouping 1} \\ \hline
Affine                          & 34        & 0.03\%
& \multirow{3}{*}{81.43\%} \\ \cline{1-3}
Neighbourhood                   & 65334     & 60.06 \%  \\ \cline{1-3}
Neighbourhood + absolute        & 23209     & 21.34\%  \\ \hline
Other                           & 20196     & 18.57 \%  \\ \hline \hline
\textbf{Total}                  & 108773    & 100\% \\
\end{tabular}
\end{center}
%
\noindent
Since, affine and neighbour patterns are static, we group them
(\textit{grouping 1}) to see that $81.43\%$ of the array computations
(88,577) have a static pattern that comprises constant offsets of
base/derived induction variables (potential with some absolute
indices), confirming \emph{hypothesis 1}. Note that affine subscripts
are rare, perhaps due to programmers relying on compilers for
optimisation rather than hand optimising (which tends to lead to
affine indices).  Overwhelmingly, the main category is neighbourhood
offsets (possibly mixed with constants in some dimensions). The
``affine + absolute'' class is not represented at all. \marginpar{\mnote{(2)
  Mention what sort of things are included in other.}}

@@

The most common category has an LHS array subscript
